%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Tanmay Modh} \\ \vspace{1pt}
    \small +91-7550176936 $|$ \href{modhtanmay@gmail.com}{\underline{modhtanmay@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/tanmay-modh-/}{\underline{LinkedIn}} $|$
    \href{https://github.com/modhtanmay}{\underline{GitHub}}
\end{center}

%
\begin{flushleft}
Technical Support Analyst with experience in application deployment, debugging, and issue resolution. Proficient in Linux, Java, and cloud technologies, focused on scalable systems and efficient software solutions.
\end{flushleft}

%-----------Technical SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Linux, SQL} \\
     \textbf{Frameworks}{: Spring Boot} \\
     \textbf{Cloud Platforms}{: AWS(EC2, S3, IAM)} \\
     \textbf{DevOps Tools}{: Docker, Git, Jenkins} \\
     \textbf{Database Managenemt}{: MySQL, Oracle Database} \\
    \textbf{Networking}{: SSH, SCP} \\
    }}
 \end{itemize}


%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2021 -- Present}
      {Temenos}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Supporting client issue of Temenos Triple A Plus modules, engaged in \textbf{troubleshooting, debugging, problem solving and root cause analysis}, while SLA targets \textbf{(SEV2 88\%, SEV3 87.5\%, SEV4\&5 80\%)}.   }
        \resumeItem{Automating operational workflows using \textbf{Shell scripting} to manage and optimize the deployments and work processes in the staging and production environments }
        \resumeItem{Analyzed defects, provided root cause reports, and collaborated with development teams to maintain valid client defect reopen goals within \textbf{7.92\%}, driving process improvement.}
        \resumeItem{Extended \textbf{on-site support} during the \textbf{Go-Live} implementations and other important phases. Involved in sharing knowledge base with the team which includes knowledge contribution to support the team’s competency and productivity.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Onsite Production Engineer}{Jan. 2024 -- Jun. 2024}
      {Eurobank Greece (Onsite through Temenos)}{Athens, Greece}
      \resumeItemListStart
        \resumeItem{ Provided Post-Live support, addressing critical challenges accross Temenos Wealth Management Modules}
        \resumeItem{Handled live incidents, deployed hotfixes and made client specific development to enhance system stability and address client’s requirements.}
        \resumeItem{Contributed configuration, solutions for P1 issues and tailored strategies to enhance operational efficiency and customer satisfaction.}
    \resumeItemListEnd

    \resumeSubheading
      {Onsite Technical Consultant}{Sep 2022 -- Nov 2022}
      {Eurobank Cyprus (Onsite through Temenos)}{Nicosia, Cyprus}
      \resumeItemListStart
        \resumeItem{Assisted in setting up new systems, applications, and software while ensuring SLAs through resolution of technical issues}
        \resumeItem{Collaborated with stakeholders for swift resolution of complex problems, leading offshore teams with regular updates}
      \resumeItemListEnd

     \resumeSubheading
      {Programmer Analyst}{Feb 2020 -- Jun 2021}
      {Cognizant}{Pune, India}
      \resumeItemListStart
        \resumeItem{Collaborated with cross-functional teams to define design and ship new features.}
        \resumeItem{Maintained clean and efficient code to meet project requirements.}
        \resumeItem{Provided technical support and troubleshooting assistance to end-users when needed.}
      \resumeItemListEnd  

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Order Monitoring Tool} $|$ \emph{Java, SpringBoot, Linux, Oracle database, Docker}}{Nov 2024 -- Dec 2024}
          \resumeItemListStart
            \resumeItem{Developed a web application using springboot that monitors the orders created in the server}
            \resumeItem{Used SSH connection to connect Linux server}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{StockTrad-Z} $|$ \emph{Docker, Jenkins, Java, Maven, AWS, MySQL}}{Jun 2024 -- Sep 2024}
          \resumeItemListStart
            \resumeItem{Developed a web based Stock Trading Platform}
            \resumeItem{Hosted using AWS EC2 instance, deployed using Docker file and created CI/CD pipeline using Jenkins}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM University}{Chennai, India}
      {Computer Science and Engineering, BTech}{Aug. 2016 -- May 2020}
  \resumeSubHeadingListEnd



\end{document}
